data_cleaning_longer_period

### 2025-02-21 code/manuscript_data_cleaning.Rmd
final code updates

census %>% 
  filter(YEAR == 2022) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()
```

@@

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.6b <- uds.quality.6b %>% 
  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(BHCMIS.ID, STATE) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID"))

@@

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.7 <- uds.quality.7 %>% 
  inner_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(ModernGranteeID, STATE) %>% unique(), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  mutate(Race = ifelse(Race == '-', NA, Race),
         Ethnicity = ifelse(Ethnicity == '-', NA, Ethnicity))

@@

uds.quality.7 <- uds.quality.7 %>% 
   inner_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  arrange(Year, BHCMIS.ID, GrantNumber) %>% 
  mutate(BHCMISID = ifelse(is.na(BHCMISID), BHCMIS.ID, BHCMISID))

@@

@@

fins.revenue.expenses <- ufins

@@

## Write the file
```{r}
# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")

>>>>

census %>% 
  filter(YEAR == 2022) %>% 
  select(ZipCode) %>% 
  #unique() %>% 
  table() %>% 
  table()

#write_csv(census, "/Users/jhm65/Dropbox/OtherData/Emergency/ACS - Tract/ACS_zips.csv")
```

@@

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.6b <- uds.quality.6b %>% 
  left_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(BHCMIS.ID, STATE) %>% unique(), by = c("BHCMISID" = "BHCMIS.ID"))

@@

## Removes FQHCs that were not open during those first 3 years of the study period
uds.quality.7 <- uds.quality.7 %>% 
  left_join(uds.cw %>% mutate(STATE = toupper(STATE)) %>% unique() %>% mutate(STATE = ifelse(BHCMIS.ID == '010530', 'ME', 
                                                                                       ifelse(BHCMIS.ID == '090090', 'AZ', STATE))) %>% 
               select(ModernGranteeID, STATE) %>% unique(), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  mutate(Race = ifelse(Race == '-', NA, Race),
         Ethnicity = ifelse(Ethnicity == '-', NA, Ethnicity))

@@

uds.quality.7 <- uds.quality.7 %>% 
   left_join(uds.cw %>% filter(Year == 2011) %>% unique() %>% select(ModernGranteeID, BHCMIS.ID), by = c("GrantNumber" = "ModernGranteeID")) %>% 
  arrange(Year, BHCMIS.ID, GrantNumber) %>% 
  mutate(BHCMISID = ifelse(is.na(BHCMISID), BHCMIS.ID, BHCMISID))

@@

ufins2 <- read_excel("//Users/markow/Dropbox/Git/UDS/UDS-2022-Full-Dataset.xlsx", sheet = "HealthCenterInfo", skip = 0) %>% select( `GrantNumber`, `BHCMISID`) %>%
  left_join(cw, by = c("GrantNumber" = "Grant Number")) %>%
  left_join(ufins.revenue.expenses, by = c("EIN" = "EIN")) %>%
  select(`GrantNumber`:EIN, form_year:fringe_rate) %>%
  left_join(ustaffing %>% select(EIN:Staff), by = c("EIN","form_year" = "Year")) %>%
  left_join(uassliabs %>% select(EIN:Liabilities), by = c("EIN","form_year" = "Year")) %>%
  rename(ModernGranteeID = `GrantNumber`,
         BHCMIS.ID = `BHCMISID`)

@@

length(unique(ufins.revenue.expenses$EIN))

fins.revenue.expenses <- ufins #rbind(ufins, ufins2) %>% unique()

uds.sites %>% 
  select(`BHCMIS ID`, `Grant Number`, `Health Center Name`)

@@

## Write the file
```{r}
# write_csv(dfc, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_analyticalfile.csv")
# write.csv(uds.sites.full, file = "/Users/markow/Dropbox/Git/Competition/data_processed/manuscript_sites_geocoded.csv")
#dfc %>% filter(Year == 2023) %>% write_csv("/Users/markow/Dropbox/Teaching/25 - Spring - MHA Quant Methods/Week 6/Week6LabData.csv")
```
